\documentclass[11pt,a4paper]{article}

\usepackage[margin=0cm]{geometry}
\usepackage{tikz}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}

\pagestyle{empty}

% ================= COLORS =================
\definecolor{sidebar}{HTML}{2F4663}
\definecolor{light}{HTML}{F4F4F4}

% ================= SETTINGS =================
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=2pt}

\begin{document}
	
	% ================= SIDEBAR BACKGROUND =================
	\begin{tikzpicture}[remember picture,overlay]
		\fill[sidebar] (current page.north west)
		rectangle ([xshift=6.6cm]current page.south west);
	\end{tikzpicture}
	
	\vspace*{1cm}
	
	% ======================================================
	% LEFT COLUMN
	% ======================================================
	\begin{minipage}[t]{0.34\textwidth}
		\color{white}
		
		% ---- inner padding ----
		\hspace{0.3cm}
		\begin{minipage}[t]{0.82\linewidth}
			\raggedright
			
			{\LARGE \textbf{Nicolas Guerrero}}\\
			{\LARGE \textbf{Callejas}}
			
			\vspace{0.5cm}
			
			\vspace{0.2cm}
			{\color{sidebar}
				\setlength{\fboxsep}{6pt}
				\colorbox{white}{
					\parbox{0.9\linewidth}{
						\centering\small\textbf{QA AUTOMATION ENGINEER}
				}}
			}
			\vspace{0.2cm}
			
			\vspace{1cm}
			
			{\large \textbf{CONTACT}}
			
			\vspace{0.35cm}
			
			\faPhone\quad (+57) 3102039043\\[7pt]
			\faEnvelope\quad nguerrero699@gmail.com\\[7pt]
			\faMapMarker*\quad Bogota\\[7pt]
			\faLinkedin\quad\href{https://www.linkedin.com/in/nicolas-guerrero-callejas-348923201/}{\nolinkurl{linkedin.com/in/nicolas-guerrero}}
			
			\vspace{1cm}
			
			{\large \textbf{ABOUT ME}}
			
			\vspace{0.35cm}
			\footnotesize
			I’m passionate about technology, automation, and building high-quality solutions that make a real impact. \\
			I enjoy learning, collaborating, and exploring tools that optimize both development and testing processes. \\
			I love working with automation frameworks and creating efficient, scalable, and high-quality solutions that make a real impact.
			
			\vspace{1cm}
			
			{\large \textbf{INTEREST}}
			
			\vspace{0.35cm}
			\footnotesize
			I am deeply interested in software quality and automation, with a strong focus on creating efficient and maintainable testing architectures that contribute to reliable, highperforming applications. I enjoy exploring new technologies that enhance both the testing and development processes, especially within full stack environments using Java and Python. I’m also passionate about continuous integration, agile collaboration, and fostering a culture of improvement through innovation
			and learning.
			
		\end{minipage}
	\end{minipage}
	\hfill
	% ======================================================
	% RIGHT COLUMN
	% ======================================================
	\begin{minipage}[t]{0.60\textwidth}
		\raggedright
		\color{black}
		
		% ---- right column padding ----
		\hspace{0.4cm}
		\begin{minipage}[t]{0.96\linewidth}
			
			\section*{\color{sidebar}EXPERIENCE}
			
			\textbf{Software Test Analyst – GFT Technologies}\\[0.5cm]
			\textit{\underline{Client Bancolombia (2021/09–Present)}}
			
			\begin{itemize}[leftmargin=*, itemsep=2pt]
				\item Designed and maintained manual and automated tests.
				\item Developed E2E automation frameworks.
				\item API testing with Postman.
				\item CI/CD integration in Azure DevOps.
			\end{itemize}
			
			\textit{\underline{Tools:} Java, Cucumber, Serenity BDD, JMeter, Azure DevOps, Git, SQL}
			
			\vspace{0.5cm}
			
			\textit{\underline{Client Tigo (2021/04–2021/09)}}
			
			\begin{itemize}[leftmargin=*, itemsep=2pt]
				\item Developed and executed E2E automation frameworks.
				\item Performance testing.
				\item CI/CD participation.
			\end{itemize}
			
			\textit{\underline{Tools:} Java, JavaScript, Cucumber, Serenity BDD, Git, SQL}
			
			\vspace{0.8cm}
			
			\section*{\color{sidebar}FORMATION}
			
			\textbf{Universidad Distrital Francisco José de Caldas}\\
			Telematic Engineering\\ 
			(2021–2025)
			
			\vspace{0.25cm}
			
			\textbf{Universidad Distrital Francisco José de Caldas}\\
			Technologist in Data Systematization and Telematic Engineering\\ (2017–2020)
			
			\vspace{0.25cm}
			
			\textbf{Universidad Nacional de Colombia}\\
			Diploma in Programming \\
			(2020–2021)
			
			\vspace{0.25cm}
			
			\textbf{Servicio Nacional DE Aprendizaje - SENA }\\
			Technical Degree in Systems \\
			(2016)
			
			\vspace{0.8cm}
			
			\section*{\color{sidebar}LANGUAGES}
			
			\begin{itemize}[leftmargin=*]
				\item Spanish – Native
				\item English – B1
			\end{itemize}
			
		\end{minipage}
	\end{minipage}
	
\end{document}